Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved

Large-scale \cite{Bertin-Mahieux2008}. See previous work for \textit{Shingles}
papers.

@@

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event, 
or ``segment'', for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar (Figure \ref{fig:barsize}). 
Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

@@

\subsection{Artist Set}
A set of songs from $20$ artists.

@@

\subsection{Codebook}
We can present the most typical patterns (Figure \ref{fig:codes1}). 
Then, LLE? (Figure \ref{fig:lle}). 
Then, the graph on variance. (Figure \ref{fig:code_var}).

@@

\small
%\section{Acknowledgements}
%Thierry is NSERC graduate fellow, or some title like that.
% Graham for the NMF stuff, unless is an author.

>>>>

Working with large collections is a necessity.

Computationally expensive, most of the techniques developed do not scale
to hundred of thousands songs. Practical question, how to describe a music
space made of millions of songs?

Some work have tackled that problem. For instance, Bertin-Mahieux et al.
\cite{Bertin-Mahieux2008} automatically tag a collection larger than $100$K
songs. Casey and Slaney \cite{Casey2006} introduced their \textit{Shingles}
representation and perform $k$-nn over thousands of examples.

@@

\subsection{EchoNest API}
We use the Echo Nest analyze API \cite{EchoNest} throughout this work.
The API gives us a chroma vector (length $12$) for every music event (called 
``segment'') for any song we upload to their platform. 
We also get an estimate of where the beats and the bars are. Beats span over
multiple segments, and bars span over multiple beats. 
We transform the chroma vectors per segment into per beat vectors using a 
simple average. We can then stack beat vectors for a number of bars 
(usually 1 or 2). 
We get a fixed-size patch by resampling the number of chroma vectors. Typically,
there are $4$ beats per bar (Figure \ref{fig:barsize}). 
Thus an appropriate pattern size for one bar
is $12$x$4$ or $12$x$8$.

@@

\subsection{Artist Set}
This set ecompass $1402$ songs $20$ artists, mostly rock and pop of different 
subgenres. Some results were available regarding the artist recognition
task. Few details given to preserve anonymity.

@@

\subsection{Codebook}
We can present the most typical patterns (Figure \ref{fig:codes1}). 
Then, LLE\footnote{implementation: 
\url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}} 
\cite{Roweis2000}? (Figure \ref{fig:lle}). 
Then, the graph on variance. (Figure \ref{fig:code_var}).

@@

\small
%\section{Acknowledgements}
%Thierry is NSERC graduate fellow, or some title like that.
%Ron has a grant too.
% Graham for the NMF stuff and numerous discussions.
